---
title: Car Pricing
affiliation:
  ## use one only of the following
  # author-columnar: true         ## one column per author
  institution-columnar: true  ## one column per institution (multiple autors eventually)
  # wide: true                  ## one column wide author/affiliation fields
  institution:
    - name: Western Sydney University
      department: School of Computing, Engineering and Mathmatics
      location: Sydney
      email: ece@datech.edu
      mark: 1
      author:
        - name: Rabina Padhy
   
bibliography: mybibfile.bib
output: rticles::ieee_article

---
XII APPENDIX
============
packaging

```{r }
library(readr)
library(lattice)
library(tibble)
library(DAAG)
library(e1071)
```

```{r load, eval=TRUE, echo=FALSE}
data1 <- read.csv("car1.csv")
dim(data1)
```

CleanProcess

```{r carDetailsDataset}
carDetails <- subset(data1, data1$HorsePower>0)
dim(carDetails)
```

Classification
\tiny
```{r classification}
sapply(carDetails, class)
```
\normalsize

```{r dim}
dim(carDetails)
```



Converting FuelType to FuelTypeCode
\tiny
```{r FuelTypeCode}
FuelTypeCode = carDetails$FuelType
levels(FuelTypeCode)
levels(FuelTypeCode)[levels(FuelTypeCode)=="diesel"]=0
levels(FuelTypeCode)[levels(FuelTypeCode)=="gas"]=1
levels(FuelTypeCode)
FuelTypeCode = as.numeric(levels(FuelTypeCode))[FuelTypeCode]
class(FuelTypeCode)
table(FuelTypeCode)
```
\normalsize

COnverting Make to MakeCode
\tiny
```{r MakeCode}
MakeCode = carDetails$Make
levels(MakeCode)
levels(MakeCode)[levels(MakeCode)=="alfa"]=1
levels(MakeCode)[levels(MakeCode)=="audi"]=2
levels(MakeCode)[levels(MakeCode)=="bmw"]=3
levels(MakeCode)[levels(MakeCode)=="chevrolet"]=4
levels(MakeCode)[levels(MakeCode)=="dodge"]=5
levels(MakeCode)[levels(MakeCode)=="honda"]=6
levels(MakeCode)[levels(MakeCode)=="isuzu"]=7
levels(MakeCode)[levels(MakeCode)=="jaguar"]=8
levels(MakeCode)[levels(MakeCode)=="mazda"]=9
levels(MakeCode)[levels(MakeCode)=="mercedes-benz"]=10
levels(MakeCode)[levels(MakeCode)=="mercury"]=11
levels(MakeCode)[levels(MakeCode)=="mitsubishi"]=12
levels(MakeCode)[levels(MakeCode)=="nissan"]=13
levels(MakeCode)[levels(MakeCode)=="peugot"]=14
levels(MakeCode)[levels(MakeCode)=="plymouth"]=15
levels(MakeCode)[levels(MakeCode)=="porsche"]=16
levels(MakeCode)[levels(MakeCode)=="renault"]=17
levels(MakeCode)[levels(MakeCode)=="saab"]=18
levels(MakeCode)[levels(MakeCode)=="subaru"]=19
levels(MakeCode)[levels(MakeCode)=="toyota"]=20
levels(MakeCode)[levels(MakeCode)=="volkswagen"]=21
levels(MakeCode)[levels(MakeCode)=="volvo"]=22

levels(MakeCode)

table(MakeCode)
MakeCode = as.numeric(MakeCode)
class(MakeCode)

```
\normalsize

Reformat Dataset

\tiny
```{r reformat}
carDetails <- add_column(carDetails, MakeCode,FuelTypeCode, .after = 1)
carDetails = carDetails[,-1]
carDetails = carDetails[,-3]
head(carDetails)
set.seed(9001)
train<-sample(1:nrow(carDetails),150)

head(train)
CarDetrailstrain=carDetails[train, ]
dim(CarDetrailstrain)
```
\normalsize

Linear Model

\tiny
```{r LinearSummary}
LinearModel = lm(Price~EngineSize, data = carDetails, subset = train)
summary(LinearModel)
```
\normalsize


\tiny
```{r ConfidentIntervalpfLinear}
confint(LinearModel)
```
\normalsize


Linear Model Anova
\tiny
```{r LinearAnova}
anova(LinearModel)

plot(Price~EngineSize, data = carDetails, xlab="EngineSize in Cubic Inches",ylab = "Price in thousands of Australian Dollar", main="Price Vs EngineSize", col = "red", pch = 20)
abline(a= -6.76, b=0.156, col = "green", lwd = 2)
legend(100, 45, legend=c("Observation", "Linear"),
       col=c("red", "green"), c( 2, 3),cex=0.8)
```
\normalsize


PolyNomial Model
\tiny
```{r}
polyModel1=lm(Price~poly(CurbWeight,3), data = carDetails, subset = train) 
summary(polyModel1)
anova(polyModel1)
plot(Price~CurbWeight, data = CarDetrailstrain, xlab="CurbWeight in grams",ylab = "Price in thousands of Austalian Dollar", main="Price Vs CurbWeight", col = "red", pch = 20)
lines(smooth.spline(CarDetrailstrain$CurbWeight, predict(polyModel1)), col= "blue",lwd=2, lty=2,pch=10, type = "b")
legend(1500,40, legend=c("observation","Polynomial"), col=c("red","blue"), pch = c(20, 10),cex=0.8)

```
\normalsize


Interaction Model
\tiny
```{r}
InteractionModel = lm(Price~Width+CurbWeight+Width*CurbWeight, data = carDetails, subset = train)
summary(InteractionModel)
anova(InteractionModel)
plot(Price~CurbWeight, data = CarDetrailstrain,xlab="CurbWeight in grams",ylab = "Price in thousands of Austalian Dollar", main="Price Vs CurbWeight", col = "red", pch = 20)
lines(smooth.spline(CarDetrailstrain$CurbWeight,predict(InteractionModel)), col= "orange",lwd=3, pch=10, type = "b")
lines(smooth.spline(CarDetrailstrain$CurbWeight, predict(polyModel1)), col= "blue",lwd=2, lty=2,pch=15, type = "b")
legend(1500,40, legend=c("observation","Interaction", "polynomial"), col=c("red","orange", "blue"), pch = c(20, 10, 15),cex=0.8)

```
\normalsize



MultiLinear Model Summary

\tiny
```{r MultiLinearModel}
MultiLinearModel = lm(Price~EngineSize+CurbWeight+Width+MPG , data = carDetails, subset = train)
summary(MultiLinearModel)
anova(MultiLinearModel)
plot(Price~EngineSize, data = CarDetrailstrain, xlab="EngineSize in Cubic Inches",ylab = "Price in thousands of Australian Dollar", main="Price Vs EngineSize", col = "red", pch = 20)
abline(a= -6.385, b=0.152, col = "green", lwd = 2)
lines(smooth.spline(CarDetrailstrain$EngineSize, predict(MultiLinearModel)), col= "blue",lwd=2, lty=2,pch=15, type = "b")
legend(100, 45, legend=c("Observation", "Linear", "MultipleLinear"),
       col=c("red", "green", "blue"), c( 2, 3, 4),cex=0.8)
```
\normalsize

Hybrid Model
\tiny
```{r }
selectModel = lm(Price~EngineSize+Width+CurbWeight+Width*CurbWeight+I(CurbWeight*CurbWeight) , data = carDetails, subset = train)
summary(selectModel)

anova(selectModel)
par(mfrow=c(2,2))
plot(selectModel)

```
\normalsize

Crossvaidation
\tiny
```{r}
dim(carDetails[-train,])

carDetailstest <- carDetails[-train,]
carDetailstest <- rbind(carDetailstest, carDetails[-train,])
carDetailstest <- rbind(carDetailstest, carDetails[-train,])

dim(carDetailstest)

cv.lm(data = carDetailstest, selectModel, m= 10)
```
\normalsize


Claasification
```{r}
data2<- sample(1: nrow(carDetails), 200)
carDetailsClass <- carDetails[data2,]
dim(carDetailsClass)
```

Price to HighPrice

\tiny
```{r eval=TRUE}

HighPrice = ifelse(carDetailsClass$Price <= 13.17, "No", "Yes")

HighPrice <- factor(HighPrice)
carDetailsClass <- add_column(carDetailsClass, HighPrice, .after = 15)

HighPriceCode = carDetailsClass$HighPrice
levels(HighPriceCode)
table(HighPriceCode)
table(HighPrice)
levels(HighPriceCode)[levels(HighPriceCode)=="No"]=0
levels(HighPriceCode)[levels(HighPriceCode)=="Yes"]=1
levels(HighPriceCode)
HighPriceCode <- as.numeric(levels(HighPriceCode))[HighPriceCode]
table(HighPriceCode)
```
\normalsize

Reformat Data
\tiny
```{r}
head(carDetailsClass)
carDetailsClass <- add_column(carDetailsClass, HighPriceCode, .after = 15)
carDetailsClass = carDetailsClass[,-17]

head(carDetailsClass)
colnames(carDetailsClass)
```
\normalsize

Get Train and Test
\tiny
```{r}
set.seed(9003)
trainClass<-sample(1:nrow(carDetailsClass),100)
testClass<-carDetailsClass[-trainClass,]

HighPrice.train=HighPrice[trainClass]
HighPrice.test=HighPrice[-trainClass]

carDetailsClassTrain <- carDetailsClass[trainClass,]
dim(carDetailsClassTrain)
head(carDetailsClassTrain)
carDetailsClassTest <- testClass
dim(carDetailsClassTest)

```
\normalsize

Linear Logistic Model
\tiny
```{r}
LinearLogisticMod=glm(HighPriceCode~EngineSize, data = carDetailsClassTrain, family=binomial)
summary.glm(LinearLogisticMod)


```
\normalsize

Training dataset linear
```{r}
glm_prob<-predict(LinearLogisticMod, type="response")

glm_pred<- rep("No", 100)
glm_pred[glm_prob>0.5]="Yes"

table(glm_pred,HighPrice.train)

table(glm_pred,HighPrice.test)
```

polylogstic model
\tiny
```{r}
PolyLogisticMod=glm(HighPriceCode~poly(EngineSize,3), data = carDetailsClassTrain, family=binomial)
summary.glm(PolyLogisticMod)
glm_prob1<-predict(PolyLogisticMod, type="response")

glm_pred1<- rep("No", 100)
glm_pred1[glm_prob1>0.5]="Yes"

table(glm_pred1,HighPrice.train)

table(glm_pred1,HighPrice.test)
```
\normalsize

interaction logistic model
\tiny
```{r}
InteractionLogisticMod=glm(HighPriceCode~Width+CurbWeight+Width*CurbWeight, data = carDetailsClassTrain, family=binomial)
summary.glm(InteractionLogisticMod)
glm_prob2<-predict(PolyLogisticMod, type="response")

glm_pred2<- rep("No", 100)
glm_pred2[glm_prob2>0.5]="Yes"

table(glm_pred2,HighPrice.train)

table(glm_pred2,HighPrice.test)
```
\normalsize

Multilinear logistic model
\tiny
```{r}
MultiLogisticMod=glm(HighPriceCode~EngineSize+CurbWeight+Width+MPG, data = carDetailsClassTrain, family=binomial)
summary.glm(MultiLogisticMod)
glm_prob3<-predict(MultiLogisticMod, type="response")

glm_pred3<- rep("No", 100)
glm_pred3[glm_prob3>0.5]="Yes"

table(glm_pred3,HighPrice.train)

table(glm_pred3,HighPrice.test)
```
\normalsize

Selection model
\tiny
```{r}
HybridlogicModel = glm(HighPriceCode~EngineSize+MPG, data = carDetailsClassTrain, family=binomial)
summary.glm(HybridlogicModel)

glm_prob4<-predict(HybridlogicModel, type="response")

glm_pred4<- rep("No", 100)
glm_pred4[glm_prob4>0.5]="Yes"

table(glm_pred4,HighPrice.train)

table(glm_pred4,HighPrice.test)

anova(HybridlogicModel)
```
\normalsize


PCA
\tiny
```{r}
par(mfrow=c(3,2))
plot(WheelBase~Length, data=carDetailsClass,
     col=unclass(HighPrice)+1, pch=16)
plot(Width~CurbWeight, data=carDetailsClass,
     col=unclass(HighPrice)+1, pch=16)
plot(EngineSize~HorsePower, data=carDetailsClass,
     col=unclass(HighPrice)+1, pch=16)
plot(Bore~Stroke, data=carDetailsClass,
     col=unclass(HighPrice)+1, pch=16)
plot(CompressionRatio~MPG, data=carDetailsClass,
     col=unclass(HighPrice)+1, pch=16)
plot(PeakRPM~Height, data=carDetailsClass,
     col=unclass(HighPrice)+1, pch=16)
```
\normalsize

Reformat dataset
\tiny
```{r}
View(carDetailsClass)
carDetailsClass = carDetailsClass[,-8]

carDetailsClass_new <- carDetailsClass[,3:5]

carDetailsClass_new <- cbind(carDetailsClass_new, carDetailsClass[,7])
carDetailsClass_new <- cbind(carDetailsClass_new, carDetailsClass[,8])
head(carDetailsClass_new)
carDetailsClass_new <- cbind(carDetailsClass_new, carDetailsClass[,12])
carDetailsClass_new <- cbind(carDetailsClass_new, carDetailsClass[,9:10])
carDetailsClass_new <- cbind(carDetailsClass_new, carDetailsClass[,11])
carDetailsClass_new <- cbind(carDetailsClass_new, carDetailsClass[,14])
carDetailsClass_new <- cbind(carDetailsClass_new, carDetailsClass[,13])
carDetailsClass_new <- cbind(carDetailsClass_new, carDetailsClass[,6])
carDetailsClass_new <- cbind(carDetailsClass_new, carDetailsClass[,16])

colnames(carDetailsClass_new) <- c("WheelBase", "Length", "Width",
                                  "CurbWeight", "EngineSize", "HorsePower" ,
                                 "Bore", "Stroke", "CompressionRatio","MPG",
                                 "PeakRPM", "Height", "HighPrice")
```
\normalsize

PCA Perform
\tiny
```{r}
carDetailsClass_new <- subset(carDetailsClass_new, carDetailsClass_new$Bore>0)
View(carDetailsClass_new)
obj3 = prcomp(carDetailsClass_new[,1:12]) # perform PCA
par(mfrow=c(3,2))
obj3 = prcomp(carDetailsClass_new[,1:12]) # perform PCA
plot(obj3$x[,1:2], col=unclass(carDetailsClass_new$HighPrice)+1,pch=16, asp=1)
plot(obj3$x[,3:4], col=unclass(carDetailsClass_new$HighPrice)+1,pch=16, asp=1)
plot(obj3$x[,5:6], col=unclass(carDetailsClass_new$HighPrice)+1,pch=16, asp=1)
plot(obj3$x[,7:8], col=unclass(carDetailsClass_new$HighPrice)+1,pch=16, asp=1)
plot(obj3$x[,9:10], col=unclass(carDetailsClass_new$HighPrice)+1,pch=16, asp=1)
plot(obj3$x[,11:12], col=unclass(carDetailsClass_new$HighPrice)+1,pch=16, asp=1)

par(mfrow=c(1,1))
biplot(obj3, cex= 0.5, main = "Variance of Car Details")
summary(obj3)
obj3$center
obj3$sdev
screeplot(obj3, main = "Variance of Car Details")
obj3$sdev
pr.var3 = obj3$sdev^2
pr.var3
pve3 = pr.var3/sum(pr.var3)
pve3

par(mfrow=c(1,2))
plot(pve3,xlab="Principal Component",ylab="Proportion of Variance Explained",
     ylim = c(0,1), type = 'b')

plot(cumsum(pve3),xlab="Principal Component",ylab="Cumulative Proportion of Variance Explained",
     ylim = c(0,1), type = 'b')
```
\normalsize

Different models

Toyota
\tiny
```{r}
ToyotaCarDetails <- subset(carDetails, carDetails$MakeCode==20)
dim(ToyotaCarDetails)

ToyotaselectModel = lm(Price~EngineSize+Width+CurbWeight+Width*CurbWeight+I(CurbWeight*CurbWeight) , data = ToyotaCarDetails)
summary(ToyotaselectModel)
anova(ToyotaselectModel)
```
\normalsize

Nissan
\tiny
```{r}
NissanCarDetails <- subset(carDetails, carDetails$MakeCode==13)
dim(NissanCarDetails)
NissanselectModel = lm(Price~EngineSize+Width+CurbWeight+Width*CurbWeight+I(CurbWeight*CurbWeight) , data = NissanCarDetails)
summary(NissanselectModel)
anova(NissanselectModel)
```
\normalsize

\tiny
```{r}
MitsubishiCarDetails <- subset(carDetails, carDetails$MakeCode==12)
dim(MitsubishiCarDetails)

MitsubishiselectModel = lm(Price~EngineSize+Width+CurbWeight+Width*CurbWeight+I(CurbWeight*CurbWeight) , data = MitsubishiCarDetails)
summary(MitsubishiselectModel)
anova(MitsubishiselectModel)
```
\normalsize

comepare
\tiny
```{r}
par(mfrow=c(1,3))

plot(Price~EngineSize, data = ToyotaCarDetails, xlab="EngineSize in Cubic Inches",ylab = "Price in thousands of Austalian Dollar", main="Price Vs EngineSize", col = "blue", pch = 20)
lines(smooth.spline(ToyotaCarDetails$EngineSize,predict(ToyotaselectModel)), col= "blue",lwd=2, lty=1)
par(new = TRUE)
plot(Price~EngineSize, data = NissanCarDetails, xlab="EngineSize in Cubic Inches",ylab = "Price in thousands of Austalian Dollar", main="Price Vs EngineSize", col = "green", pch = 20)
lines(smooth.spline(NissanCarDetails$EngineSize,predict(NissanselectModel)), col= "green",lwd=2, lty=1)
par(new = TRUE)
plot(Price~EngineSize, data = MitsubishiCarDetails, xlab="EngineSize in Cubic Inches",ylab = "Price in thousands of Austalian Dollar", main="Price Vs EngineSize", col = "red", pch = 20)
lines(smooth.spline(MitsubishiCarDetails$EngineSize,predict(MitsubishiselectModel)), col= "red",lwd=2, lty=1)
legend(100, 14, legend=c("Totota", "Nissan", "Mitsubishi"),col=c("green", "blue", "red"), c( 3, 4, 2), cex=0.8)



plot(Price~CurbWeight, data = ToyotaCarDetails, xlab="CurbWeight in grams",ylab = "Price in thousands of Austalian Dollar", main="Price Vs CurbWeight", col = "blue", pch = 20)
lines(smooth.spline(ToyotaCarDetails$CurbWeight,predict(ToyotaselectModel)), col= "blue",lwd=2, lty=1)
par(new = TRUE)
plot(Price~CurbWeight, data = NissanCarDetails, xlab="CurbWeight in gramss",ylab = "Price in thousands of Austalian Dollar", main="Price Vs CurbWeight", col = "green", pch = 20)
lines(smooth.spline(NissanCarDetails$CurbWeight,predict(NissanselectModel)), col= "green",lwd=2, lty=1)
par(new = TRUE)
plot(Price~CurbWeight, data = MitsubishiCarDetails, xlab="CurbWeight in grams",ylab = "Price in thousands of Austalian Dollar", main="Price Vs CurbWeight", col = "red", pch = 20)
lines(smooth.spline(MitsubishiCarDetails$CurbWeight,predict(MitsubishiselectModel)), col= "red",lwd=2, lty=1)
legend(2000, 14, legend=c("Totota", "Nissan", "Mitsubishi"),col=c("green", "blue", "red"), c( 3, 4, 2), cex=0.5)

plot(Price~Width, data = ToyotaCarDetails, xlab="Width in centimeter",ylab = "Price in thousands of Austalian Dollar", main="Price Vs Width", col = "blue", pch = 20)
lines(smooth.spline(ToyotaCarDetails$Width,predict(ToyotaselectModel)), col= "blue",lwd=2, lty=1)
par(new = TRUE)
plot(Price~Width, data = NissanCarDetails, xlab="Width in centimeter",ylab = "Price in thousands of Austalian Dollar", main="Price Vs Width", col = "green", pch = 20)
lines(smooth.spline(NissanCarDetails$Width,predict(NissanselectModel)), col= "green",lwd=2, lty=1)
par(new = TRUE)
plot(Price~Width, data = MitsubishiCarDetails, xlab="Width in centimeter",ylab = "Price in thousands of Austalian Dollar", main="Price Vs Width", col = "red", pch = 20)
lines(smooth.spline(MitsubishiCarDetails$Width,predict(MitsubishiselectModel)), col= "red",lwd=2, lty=1)
legend(65, 14, legend=c("Totota", "Nissan", "Mitsubishi"),col=c("green", "blue", "red"), c( 3, 4, 2), cex=0.8)

```
\normalsize

SVM
```{r}
carDetailsClassnew <- carDetailsClass_new

HighPriceCode1 = carDetailsClassnew$HighPrice
levels(HighPriceCode1)
table(HighPriceCode1)
table(HighPrice)
levels(HighPriceCode1)[levels(HighPriceCode1)=="No"]=0
levels(HighPriceCode1)[levels(HighPriceCode1)=="Yes"]=1
levels(HighPriceCode1)

HighPriceCode1 <- as.numeric(levels(HighPriceCode1))[HighPriceCode1]


carDetailsClassnew <- add_column(carDetailsClassnew, HighPriceCode1, .after = 12)

head(carDetailsClassnew)
carDetailsClassnew <- carDetailsClassnew[,-14]
View(carDetailsClassnew)


```

